1000 Graphs

### 2021-06-24 graphs_newt_snakes/fig_1000.Rmd
I had ran a 1000 gen simulation and had mixed up the variables. Then, I had fixed it an reran it. Next, I did an experiment where I used the variables in both the msprime and the slim script. This update if mosly for the R script to see how different the phenotypes are. I also fixed parsing do that it would work on the cluster.

@@

@@

@@

  file <- read.table(current_file, header = TRUE)
  print(max(file$Newt_max_Pheno))
  print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
```

>>>>

I made a mistake. I switched the mutation rates and the effect sizes

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)

  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}
  print(newt_max_pheno)
  print(snake_max_pheno)
```
## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

This is the correct one
```{r pressure, echo=FALSE}
newt_max_pheno = 0
snake_max_pheno = 0

@@

for (current_file in files){
  #print(current_file)

  file <- read.table(current_file, header = TRUE)
  #print(max(file$Newt_max_Pheno))
  #print(max(file$Snake_max_Pheno))
  if (max(file$Newt_max_Pheno) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)
```
## The Figure
Loop through the files and find the max and min of each of the species pheotypes
Then set up a graph with the max max
Loop though the files and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked.

files <- list.files(path="~/Desktop/pheno_test_1000_2/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  print(max(file$Newt_max_Pheno, na.rm = TRUE))
  print(max(file$Snake_max_Pheno, na.rm = TRUE))
  if (max(file$Newt_max_Pheno, na.rm = TRUE) > newt_max_pheno){
    newt_max_pheno = max(file$Newt_max_Pheno, na.rm = TRUE) }

  if (max(file$Snake_max_Pheno, na.rm = TRUE) > snake_max_pheno){
    snake_max_pheno = max(file$Snake_max_Pheno, na.rm = TRUE) }
}

  print(newt_max_pheno)
  print(snake_max_pheno)
```
some of these values are in quotes, why?

Some other things that might be goo to look at:
The average of the phenotypes
The difference between the average phenotypes
